\documentclass[11pt]{letter}

\usepackage{times,,xspace,amsmath,amssymb,color}
\usepackage[english]{babel}
\parindent=0cm
\parskip=0.28cm
\setlength{\textwidth}{17cm}
\setlength{\oddsidemargin}{-0.24cm}
\setlength{\evensidemargin}{-0.24cm}
\setlength{\topmargin}{0cm}
\setlength{\headheight}{0cm}
\setlength{\textheight}{24cm}
\setlength{\headsep}{0cm}
\newcommand{\eat}[1]{}
\date{}

\newcommand{\sstab}{\rule{0pt}{8pt}\\[-3.4ex]}
\newcommand{\stab}{\rule{0pt}{8pt}\\[-2.4ex]}
\newcommand{\vs}{\vspace{1ex}}
\newcommand{\svs}{\vspace{0.36ex}}
\newcommand{\kw}[1]{{\ensuremath {\mathsf{#1}}}\xspace}
\newcommand{\dist}{\kw{dist}}
\newcommand{\pred}{\kw{pred}}
\newcommand{\desc}{\kw{desc}}
\newcommand{\pSim}{\kw{Match}}
\newcommand{\at}[1]{\protect\ensuremath{\mathsf{#1}}\xspace}

\newcommand{\NP}{\kw{NP}}
\newcommand{\DAGs}{{\sc dag}s\xspace}
\newcommand{\NC}{\kw{NC}\xspace}
\newcommand{\coNP}{co\kw{NP}\xspace}
\newcommand{\PTIME}{\kw{PTIME}}
\newcommand{\PSPACE}{\kw{PSPACE}}
\newcommand{\EXPTIME}{\kw{EXPTIME}\xspace}
\newcommand{\NPSPACE}{\kw{NPSPACE}\xspace}


\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\im}{\item}
\newenvironment{tbi}{\begin{itemize}
        \setlength{\topsep}{1.5ex}\setlength{\itemsep}{0ex}\vspace{-0.5ex}}
        {\end{itemize}\vspace{-0.5ex}}
\newenvironment{tbe}{\begin{enumerate}
        \setlength{\topsep}{0ex}\setlength{\itemsep}{-0.7ex}\vspace{-1ex}}
        {\end{itemize}\vspace{-1ex}}

\newcommand{\eps}{\prec}
\newcommand{\deps}{\prec_{D}}
\newcommand{\leps}{\prec_L}
\newcommand{\dleps}{\prec_{D}^{L}}
\newcommand{\iso}{\lhd}
\newcommand{\bieps}{\sim}
\newcommand{\embed}{\lessdot}
\newcommand{\neps}{\ntrianglelefteq}
\newcommand{\ees}{\preceq_{(e,e)}}
\newcommand{\nees}{\not\preceq_{e,e}}
\newcommand{\Reps}{S}
\newcommand{\bcp}{{\sc bcp}\xspace}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\aka}{\emph{a.k.a.}\xspace}
\newcommand{\kwlog}{\emph{w.l.o.g.}\xspace}


\definecolor{gray}{rgb}{0.5,0.5,0.5}
\newcommand{\added}[1]{\textcolor{blue}{#1}}
\newcommand{\changed}[1]{\textcolor{red}{#1}}
\newcommand{\removed}[1]{\textcolor{gray}{#1}}

\newcommand{\ball}[1]{\hat{G}[#1]}
\newcommand{\amazon}{\kw{Amazon}}
\newcommand{\Amazon}{\kw{Amazon}}
\newcommand{\youtube}{\kw{YouTube}}
\newcommand{\YouTube}{\kw{YouTube}}


\newcommand{\match}{\kw{Match}}
\newcommand{\optmatch}{\kw{Match^+}}
\newcommand{\dismatch}{\kw{dMatch}}
\newcommand{\optdismatch}{\kw{dMatch^+}}
\newcommand{\minq}{\kw{minQ}}
\newcommand{\graphsim}{\kw{Sim}}
%\newcommand{\subiso}{\kw{SubIso}}
%\newcommand{\dissubiso}{\kw{dSubIso}}
\newcommand{\metis}{{\sc Metis}\xspace}
\newcommand{\vf}{\kw{VF2}}
\newcommand{\tale}{\kw{TALE}}
\newcommand{\mcs}{\kw{MCS}}
\newcommand{\dsim}{\kw{dSim}}
\newcommand{\dissubiso}{\kw{dVF2}}
\newcommand{\dvf}{\kw{dVF2}}

\newcommand{\stitle}[1]{\vspace{0.5ex} \noindent{\bf #1}}
\newcommand{\etitle}[1]{\vspace{1ex}\noindent{\underline{\em #1}}}

\newcommand{\ah}{{\sc ah}\xspace}
\newcommand{\alt}{{\sc alt}\xspace}
\newcommand{\tedi}{{\sc tedi}\xspace}
\newcommand{\arcflag}{{\sc arcFlag}\xspace}
\newcommand{\tnr}{{\sc tnr}\xspace}
\newcommand{\dra}{{\sc dra}\xspace}
\newcommand{\dras}{{\sc dra}s\xspace}
\pagestyle{empty}
\begin{document}
\noindent
Prof. Christian S. Jensen,\\
Editor-in-Chief,\\
ACM Transactions on Database Systems

\vspace{0.1cm}
\noindent
Dear Prof. Jensen,

\vspace{0.1cm}
\noindent
We are submitting our manuscript
``{\em Error Bounded Line Simplification Algorithms for  Trajectory Compression: An Experimental Evaluation}'',
authored by Xuelian Lin, Shuai Ma, Jiahao Jiang, Yanchen Hou, and Tianyu Wo
for possible publication in ACM TODS  as a survey article.

\medskip
\noindent
In this manuscript, we present a systematic experimental evaluation of representative error bounded line simplification algorithms, including both compression optimal and sub-optimal methods, in terms of commonly adopted perpendicular Euclidean, synchronous Euclidean and direction-aware distances.  Empirical studies of trajectory compression algorithms have been conducted. However, important aspects of trajectory simplification (compression ratios, running time and aging friendliness) are not systematically studied. That is to say, a systematic experimental evaluation of line simplification algorithms for trajectory compression remains necessary for practitioners to decide the appropriate algorithms and distance metrics for specific applications.



\medskip
\noindent
The manuscript is prepared according to the ACM TODS guidelines and
is ready for double-blind reviewing: we removed  the authors' names, and
affiliations and funding sources. Further, although we have cited our own published papers [14] and [15], we have properly handled to avoid the disclosure in this survey manuscript.

%\vspace{0.5ex}
\begin{small}
\noindent
[14] Lin, X., Jiang, J., Ma, S., Zuo, Y., and Hu, C. One-pass trajectory simplification using the synchronous euclidean
distance. VLDBJ 28, 6 (2019), 897--921.

\noindent
[15] Lin, X., Ma, S., Zhang, H., Wo, T., and Huai, J. One-pass error bounded trajectory simplification. PVLDB 10, 7 (2017),
841--852.
\end{small}





%This manuscript extends the conference version in various ways:

%\begin{itemize}
%\item We now provide detailed  proofs of all our results; These
%proofs are interesting on their own and illustrate nicely
%the subtleties involved in our analyses; and

%\item The description of various concepts is expanded, improving in this
%way the readability of the paper.
%\end{itemize}



%\medskip
\noindent
As requested, we would like to point out the following conflicts of interest:

\vspace{-0.5ex}
\begin{description}
\item[Past or present association as thesis advisor or thesis student]
Wenfei Fan,  Floris Geerts, Jinpeng Huai, Jia Li, Liang Duan.
\item[Collaboration on a project, article, or paper within the last 48 months]
Charu C. Aggarwal, Sourav S. Bhowmick, Yang Cao, Gao Cong, Kaiyu Feng, Yansong Feng,  Xiaofeng Gao,
 Peter Garraghan,   Minyi Guo, Tao Guo, Chunming Hu, Renjun Hu,  Chao Li, Jianxin Li,  Zhoujun Li, Gang Lin£¬ Junfeng Liu, Shujie Liu,
Mu Li, Tiejun Ma,  Nikos Ntarmos,  Rahul Pandita,  Saket Sathe,  Shuo Shang,  Peter Triantafillou,  Haixun Wang, Luoshu Wang, Senzhang Wang, 	Yuandong Wang, Yuanyang Wang,   Yu Wu,  Jie Xu, Bin Yao,  Renyu Yang, Hongzhi Yin, Xiaoming Zhang,  	Tao Xie, Lixiao Zheng,  Kai Zheng, Ming Zhou, Yimeng Zuo.
\end{description}

%\vspace{0.1cm}
\noindent
We look forward to a favorable review.

%\vspace{0.1cm}
\noindent
Sincerely,

%\vspace{0.2cm}
\noindent
Xuelian Lin, Shuai Ma, Jiahao Jiang, Yanchen Hou, and Tianyu Wo.


\end{document}

