%IEEEbiography

\begin{IEEEbiography}{Liang Duan} is a PhD student in the School of Computer Science and Engineering, Beihang University, supervised by Prof. Shuai Ma. He received his MS degree in computer software and theory from Yunnan University in 2014, and BS degree in computer science and technology from Beihang University in 2009. His current research interests include databases and social data analysis.
\end{IEEEbiography}

\begin{IEEEbiography}{Charu Aggarwal} received the BS degree
from IIT Kanpur in 1993 and the PhD degree
from Massachusetts Institute of Technology in
1996. He is a research scientist at the IBM T.J.
Watson Research Center in Yorktown Heights,
New York. He has since worked in the field of
performance analysis, databases, and data mining.
He has published more than 155 papers in
refereed conferences and journals, and has been
granted over 50 patents. He has served on the
program committees of most major database/
data mining conferences, and served as program vice-chairs of the
SIAM Conference on Data Mining, 2007, the IEEE ICDM Conference,
2007, the WWW Conference 2009, and the IEEE ICDM Conference,
2009. He served as an associate editor of the IEEE Transactions on
Knowledge and Data Engineering Journal from 2004 to 2008. He is an
associate editor of the ACM TKDD Journal, an action editor of the Data
Mining and Knowledge Discovery Journal, an associate editor of the
ACM SIGKDD Explorations, and an associate editor of the Knowledge
and Information Systems Journal. He is a fellow of the IEEE for
¡°contributions to knowledge discovery and data mining technique¡±, and
a life member of the ACM.
\end{IEEEbiography}


\begin{IEEEbiography}{Shuai Ma} is a professor at the School of Computer Science and Engineering, Beihang University, China.
He obtained his PhD degrees from University of Edinburgh in 2010, and from
Peking University in 2004, respectively.
He was a postdoctoral research fellow in the database group, University of Edinburgh, a summer intern at Bell labs, Murray Hill, USA and a visiting researcher of MRSA.
He is a recipient of the best paper award for VLDB 2010 and the best challenge paper award for WISE 2013. His current research interests include database theory and systems, social data and graph analysis, and data intensive computing.
\end{IEEEbiography}
\vspace{-6ex}


%\begin{IEEEbiography}{Renjun Hu}
%Biography text here.
%\end{IEEEbiography}

\vspace{-6ex}
\begin{IEEEbiography}{Jinpeng Huai} is a professor at the School of Computer Science and Engineering, Beihang University, China. He received his Ph.D. degree in computer science from Beihang University, China, in 1993. Prof. Huai is an academician of Chinese Academy of Sciences and the vice honorary chairman of China Computer Federation (CCF). His research interests include big data computing, distributed systems, virtual computing, service-oriented computing, trustworthiness and security.
\end{IEEEbiography}
