%\vspace{-1ex}
\section*{{Appendix: Semantic Based Trajectory Compression Algorithms}}
{Apart from the techniques evaluated in this article, there exist other approaches for various requirements of trajectory compression. We introduce the semantic based methods, one of the most important types of methods.}

{The trajectories of certain moving objects in urban areas, such as cars and trucks, are constrained by road networks. Hence, there are trajectory compression methods based on road networks \cite{Chen:Trajectory, Popa:Spatio,Civilis:Techniques,Hung:Clustering, Kellaris:Map, Song:PRESS, Han:Compress, Cao:Road, Li:Uncertain} that first project trajectory points onto roads (known as map-matching \cite{Quddus:MapMatching}), then compress the matched data points by \emph{piece-wise linear approximation} methods \cite{Elmeleegy:Stream, Xie:Stream,Luo:Streaming,ORourke:Fitting}. 
Note that {(1) map-matching is thought an effective way to improve the quality of a raw uncertain trajectory \cite{Li:Uncertain}, and (2)} dilution-matching-encoding \cite{Gotsman:Compaction} is an exception of such methods in that it first simplifies the original trajectory points by some line simplification method, then it projects the simplified points onto roads.}
%
{Some methods \cite{Schmid:Semantic, Richter:Semantic} compress trajectories making use of other domain knowledge, such as places of interests (POI) along the trajectories \cite{Richter:Semantic}, and the high frequency patterns of compressed trajectories instead of roads \cite{Gotsman:Compaction, Song:PRESS, Han:Compress,Koide:CiNCT}, to improve the compression effectiveness.}
%
{The location information from sensors is usually imprecise, and may be noisy and error prone \cite{Cao:Road}, while map-matching is believed able to correct the error by ``snapping'' data points onto the road network. Further, they are able to represent a trajectory basing on long paths (a path is a sequence of roads connected one by one), and to further mine the frequency patterns, so as to improve the overall compression of trajectories.}
%
{However, users should keep in mind that the effectiveness of these semantic based methods highly depends on the quality of semantic information (\eg road networks) and sequence labeling (\eg map-matching) algorithms. In some cases, \eg when the road network is not up to date or there is no road nearby or moving objects actually move along the parallel roads (but outside of the roads), these methods may result in incorrect map-matching, and introduce extra errors.}
%{Besides, sequence labeling has higher time/space consuming compared with line simplification. }
%These limitations make them be better running in server side rather than in resource constraint end devices that some line simplification algorithms are applicable.

{We believe that the semantic based methods and the line simplification methods are orthogonal, and may be combined with each other to improve the effectiveness of trajectory compression \cite{Lin:Cised}, like the way that dilution-matching-encoding \cite{Gotsman:Compaction} does.}

%\todo{compression ratio or information saved}


