\section{Introduction}
\label{sec-intro}


We study the {\em node-to-node shortest path} ({\em distance}) problem on large graphs: given a weighted undirected graph $G(V, E)$ with non-negative edge weights, and two nodes of $G$, the source $s$ and the target $t$, find the shortest path (distance) from $s$ to $t$ in $G$.
The Dijkstra's algorithm with Fibonacci heaps runs in $O(n\log n + m)$ due to Fredman \& Tarjan~\cite{CormenLRS01}, where $n$ and $m$ denote the numbers of nodes and edges in a graph, respectively, which remains asymptotically the fastest known solution on arbitrary undirected graphs with non-negative edge weights.
%The challenge of computing shortest paths on large graphs.
However, computing shortest  paths and distances remains a challenging problem, in terms of both time and space cost, on large-scale graphs. Hence, various optimizations have been developed to speed-up the computation.

To speed-up shortest  path and distance queries, our approach is to use {\em representatives}, each of which captures a set of nodes in a graph. The task of finding a proper form of representatives is {\em nontrivial}. Intuitively, we expect representatives to have the following properties.
%
(1) A small number of representatives can represent a large number of nodes in a graph;
%
(2) Shortest paths and distances involved within the set of nodes being represented by the same representative can be answered efficiently; And,
%
(3) the representatives and the set of nodes being represented can be computed efficiently.

The full version of this extended abstract appears in \cite{journal-version2016}.

\eat{%%%%%%%%%%%

\stitle{Contributions \& Roadmap}. To this end, we develop a light-weight data reduction technique for speeding-up shortest  path and distance queries on large weighted undirected graphs.

\stab (1) We first propose a notion of {\em routing proxies} (or simply proxies), each of which represents a small subgraph, referred to as  {\em deterministic routing areas} (\dras)  (Section~\ref{sec-proxy}). We also give an analysis of routing proxies and \dras, which shows that they hold good properties for speeding-up shortest path and distance queries.

\stab (2) We then develop a {\em linear-time} algorithm for computing deterministic routing areas along with their maximal routing proxies (Section~\ref{sec-proxy-algorithms}). This makes our solution a light-weight technique that is scalable to large graphs.


\stab (3) Using real-life large road and co-authorship (sparse) graphs, we finally conduct an extensive experimental study (Section~\ref{sec-expt}).
We find that (a) on average 1/3 nodes in these graphs are captured by routing proxies, leaving the reduced graph about 2/3 of the original input graph for both road and co-authorship graphs,  (b) proxies can be found efficiently, \eg they can be found in at most 6 seconds for co-authorship graphs and less than half an hour for the largest road graph, and (c) the reduced graph incurs only about 70\% space overhead of the original input graph on average.  Moreover, (d) using proxies benefits existing shortest path and distance algorithms in terms of time cost, \eg it reduces around 30\%, 20\% and 1\% time for  bidirectional Dijkstra \cite{LubyR89}, \arcflag \cite{MohringSSWW05} and \ah \cite{zhu2013shortest} on road graphs, respectively, and 49\%, 4\% and 49\% time for bidirectional Dijkstra, \arcflag and \tnr \cite{arz2013transit} on co-authorship graphs, respectively, %(e) bidirectional Dijkstra, \arcflag, \tnr and \ah with proxies scale well with respect to graph sizes,
and (e) existing shortest path and distance algorithms also benefit from using proxies in terms of space overhead, \eg\ it reduces about 62\%, 28\% and 18\% space overhead for \arcflag, \tnr and \ah on road graphs, respectively, and about 86\% and 2\% space overhead for \arcflag and \tnr on co-authorship graphs, respectively.
%
(f) Using synthetic data, we further find that proxies and \dras are sensitive to the density and degree distribution of graphs and perform well on graphs that follow the power law distribution, and, moreover, for a given degree distribution, less nodes are captured when the average degree is higher.

}%%%%%%%%%%%%%%%%%%%



%These make proxies and their \dras are a light-weight preprocessing technique for speeding-up shortest  path and distance queries.


%\sstab (3) We introduce the {\em bounded graph partitioning} problem (\gdp) to deal with the remaining subgraph that cannot be captured by the \dras of agents, and show that the problem is \NP-complete (Section~\ref{sec-decomposition}). We then propose a notion of {\em \super} graphs that combine graph partitions with hybrid landmark covers to support efficient shortest distance answering. We also build connections between the traditional graph partitioning problem and the \gdp problem, and utilize the traditional graph partitioning approaches, \eg\ \metis, to solve the problem. As shown by the experiments, \metis works well.


%\sstab (4) We propose a unified framework \disland for fast shortest distance query answering (Section~\ref{sec-query}), which seamlessly combines distance landmarks with agents, graphs partitions (\super graphs), and existing speed-up techniques~\cite{WuXDCZZ12,WagnerW07}.



