%IEEEbiography
\vspace{-8ex}
\begin{IEEEbiography}{Liang Duan} is a PhD student in the School of Computer Science and Engineering, Beihang University, supervised by Prof. Shuai Ma. He received his MS degree in computer software and theory from Yunnan University in 2014, and BS degree in computer science and technology from Beihang University in 2009. His current research interests include databases and social data analysis.
\end{IEEEbiography}
\vspace{-8ex}
\begin{IEEEbiography}{Charu Aggarwal} received the BS degree
from IIT Kanpur in 1993 and the PhD degree
from Massachusetts Institute of Technology in
1996. He is a research scientist at the IBM T.J.
Watson Research Center in Yorktown Heights,
New York. He has since worked in the field of
performance analysis, databases, and data mining.
He has served on the
program committees of most major database/
data mining conferences, and served as program vice-chairs of SDM 2007, ICDM 2007, WWW 2009, and ICDM
2009. He served as an associate editor of TKDE from 2004 to 2008. He is an
associate editor of TKDD, an action editor of DMKD, an associate editor of SIGKDD Explorations, and an associate editor of KAIS. He is a fellow of the IEEE and a fellow of the ACM.
\end{IEEEbiography}
\vspace{-8ex}
\begin{IEEEbiography}{Shuai Ma} is a professor at the School of Computer Science and Engineering, Beihang University, China.
He obtained his PhD degrees from University of Edinburgh in 2010, and from
Peking University in 2004, respectively.
He was a postdoctoral research fellow in the database group, University of Edinburgh, a summer intern at Bell labs, Murray Hill, USA and a visiting researcher of MRSA.
He is a recipient of the best paper award for VLDB 2010 and the best challenge paper award for WISE 2013. His current research interests include database theory and systems, social data and graph analysis, and data intensive computing.
\end{IEEEbiography}
\vspace{-8ex}
\begin{IEEEbiography}{Tiejun Ma} is an assistant Professor in Risk Analysis within Centre for Risk Research, Department of Decision Analytics and Risk at the University of Southampton. He received his PhD from University of Edinburgh. Before he joined the University of Southampton, he worked at the Department of Computing, Imperial College London and the Oxford e-Research Centre, University of Oxford to carry on research work related to quantitative modelling related to mobile network and computing systems. His research focuses on risk analysis and decision-making using quantitative modelling and real-time Big data analysis techniques applies to FinTech, Cyber-Risk, and Resilience of distributed systems.
\end{IEEEbiography}
\vspace{-8ex}
\begin{IEEEbiography}{Jinpeng Huai} is a professor at the School of Computer Science and Engineering, Beihang University, China. He received his Ph.D. degree in computer science from Beihang University, China, in 1993. Prof. Huai is an academician of Chinese Academy of Sciences and the vice honorary chairman of China Computer Federation (CCF). His research interests include big data computing, distributed systems, virtual computing, service-oriented computing, trustworthiness and security.
\end{IEEEbiography}
