
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "www2019"
%%% End:

\section{Tracking in combined areas}
\label{sec:combine}


\subsection{Combining circular and strip areas}
Position tracking and trajectory tracking both use \sed as the distance metric to check data points that confirms the actual position of a moving object at time $t$ lives in a circular area around the excepting position of the moving object at that time.
Though \sed is currently the only distance metric used in tracking moving objects, we argue that another distance metric, \ped that is wildly used trajectory compression, can also be applied in tracking moving objects that confirms a moving object lives in a strip area. More important, we can combine \sed and \ped to track a moving object in an alternative area that balances two key metrics, \ie the compression ratios and the query errors, of trajectory simplification and tracking algorithms, and satisfies the needs of varied applications.


\stitle{Binary distances of \sed and \ped, shortly BED (\sed, \ped)}, is the combination of distance metrics \sed and \ped such that (1) if $\ped \ge \sed$, then it falls back to the \sed, otherwise, (2) it is the combination of a circular and a strip areas, and forms a rectangle whose short sides are replaced by circular arcs as shown in \todo{Figure}. Note that if $\ped << \sed$, then it is actually close to the \ped.


\todo{discuss: dad?}

\subsection{Position tracking in combined areas}
based on ldr


\subsection{Trajectory tracking in combined areas}

combine cone, sector, interval with ldr; what's sector, interval.


strong tracking

-- principle, adjust velocity...
	checking \textcolor{blue}{separately} of cone, sector and interval ($P_sP_{s+k-1}$ is the choice), couple with ldr.
	step 1: check metrics: (if all intersections of one metric are true, then there must be a line segment satisfying all).
	if any intersection of one metric is false, then new line segment.
	step 2:	(check ldr) if any ldr is false, then find the common intersection of all metric and adjust velocity; select a point from the common area (or simply $P_{s+k-1}$).

-- algorithm. intersection based trajectory tracking (ITT-S)

-- example

-- correctness and complexity

weak tracking

-- principle, adjust velocity...
	must checking \textcolor{blue}{consistently} of cone, sector and interval, couple with ldr.
	if the common intersection of all metrics is false, then new line segment.
	otherwise, checks ldr, 	if any ldr is false, then adjust velocity, point select from the common area.
	
-- algorithm. intersection based trajectory tracking (ITT-W)

-- example

-- correctness and complexity

-- discuss: relations to position tracking and traj simplification.
