
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "www2019"
%%% End:

\section{Effective one-pass tracking}
\label{sec:traj}
ldr is a efficient traj tracking algorithm, suffer in compression ratio.
grts has good compression ratio, but, 1. buffer, 2. separate compression and position tracking.
Observing one-pass algorithms, cised using sed, siped using ped, interval using dad
low time complexities and good compression ratios, compared with dp...
why not integrate one-pass algorithms with GRTS? 
1. one pass algorithm do not need a buffer; 2. a one-pass algorithm runs in a manner similar with ldr, 
inspire us to develop effective and efficient trajectory tracking methods that combine compression and position tracking into a consistent algorithm, and run in one-pass manner. 

\subsection{One-pass tracking in circular areas}

spatio-temporal cone and uses it to compress traj

combine st-cone with ldr; what's cone


two algorithms: strong tracking and weak tracking

Strong tracking: 

-- principle, adjust velocity.

-- algorithm

-- example

-- correctness and complexity

Weak tracking:

-- theorem: if ldr is true, then the intersection of those cones must not be \{$P_s$\}.
means that, if ldr is true, it is sure those points can be represented by a line segment.
thus, we only need to check the intersection after ldr is false, during the process.

-- algorithm

-- example

-- correctness and complexity

\subsection{One-pass tracking in combined areas}

combine cone, sector, interval with ldr; what's sector, interval


strong tracking

-- principle, adjust velocity...
	checking \textcolor{blue}{separately} of cone, sector and interval ($P_sP_{s+k-1}$ is the choice), couple with ldr.
	step 1: check metrics: (if all intersections of one metric are true, then there must be a line segment satisfying all).
	if any intersection of one metric is false, then new line segment.
	step 2:	(check ldr) if any ldr is false, then find the common intersection of all metric and adjust velocity; select a point from the common area (or simply $P_{s+k-1}$).

-- algorithm

-- example

-- correctness and complexity

weak tracking

-- principle, adjust velocity...
	must checking \textcolor{blue}{consistently} of cone, sector and interval, couple with ldr.
	if the common intersection of all metrics is false, then new line segment.
	otherwise, checks ldr, 	if any ldr is false, then adjust velocity, point select from the common area.
	
-- algorithm

-- example

-- correctness and complexity
